Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-28 tex/MesnardoBarba2019.tex
First attempt at revising workflow section

\usepackage{listings}
\lstset{
    aboveskip=20pt,
    belowskip=20pt,
    lineskip=5pt,
    backgroundcolor=\color{white},
    basicstyle=\footnotesize\ttfamily,
    breakatwhitespace=true,
    breaklines=true,
    captionpos=none,
    extendedchars=true,
    frame=none,
    keepspaces=true,
    morekeywords={*,...},
    numbers=none,
    numbersep=5pt,
    rulecolor=\color{black},
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    stepnumber=2,
    tabsize=2,
    title=\lstname,
}

@@

Scientific publications reporting computational results often lack sufficient details to reproduce the researcher's computational environment; e.g., they may miss to mention external libraries used along with the main computational code.
We have learned the hard way how different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
To overcome the so-called ``dependency hell'' and facilitate reproducibility, we use Docker to locally create an image of our computational application.
Container technology facilitates share build images of the full software stack that is used to produce scientific results.
The process of building an image using Docker begins with writing an ASCII file, called a Dockerfile, that contains Docker keywords and system commands for building multi-layered software stack.
Once the image is build locally, we push it to a public registry (e.g., DockerHub).

\begin{lstlisting}
$ cd $CLOUDREPRO/docker/petibm
$ docker build --tag=barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu --file=Dockerfile .
$ docker push barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu
\end{lstlisting}

Everyone can now pull the application image and create a container to run the application in a faithfully reproduced local environment.
We aim to move the final stage of this workflow (creating a container) to a public cloud provider such as Microsoft Azure.

To run computational jobs on Microsoft Azure, we use several tools that facilitate creating and managing virtual machines with compute nodes and submitting jobs to those nodes.
\ref{fig:cloud_workflow} shows a graphical representation of the workflow we adopted to run CFD simulations with an in-house software on Microsoft Azure.
We use a Microsoft Azure platform service called Azure Batch to run our in-house CFD software.
Azure Batch services leverages Microsoft Azure at no extra cost to relieve the user from manually creating, configuring, and managing a HPC-capable cluster of cloud nodes, including virtual machines, virtual networks, job and task scheduling infrastructure.
Azure Batch works with both embarrassingly parallel workloads and tightly-coupled MPI jobs (the latter being the case of our CFD software).
To use Azure Batch, the user needs to configure a workspace on Microsoft Azure by creating an Azure Batch account associated to an Azure Storage account (to upload and download simulation data).
This can be done either via the Azure Portal in a web browser or from a local terminal user the open-source tool Azure CLI.\footnote{Azure CLI (version 2.0.57): \url{https://github.com/Azure/azure-cli}}

\begin{lstlisting}
$ az account set --subscription reprosubscription
$ az group create --name reprorg --location eastus
$ az storage account create --name reprostorage --resource-group reprorg --sku Standard_LRS --location eastus
$ az batch account create --name reprobatch --resource-group reprorg --location eastus --storage-account reprostorage
$ az storage share create --name fileshare --account-name reprostorage --account-key storagekey --quota 100
\end{lstlisting}

To create computational nodes and submit container-based jobs to Azure Batch, we use the open-source command-line utility Batch Shipyard.\footnote{Batch Shipyard (version 3.6.1): https://github.com/Azure/batch-shipyard} Batch Shipyard reads user-written YAML configuration files to automatically create pools of compute nodes on Microsoft Azure and to submit jobs to those pools.

@@

The Docker image of our CFD application is pulled from the (public or private) registry to the virtual machines when the pool is created.

\begin{lstlisting}
$ cd $CLOUDREPRO/examples/snake2d2k35
$ az storage directory create --name snake2d2k35 --share-name fileshare --account-name reprostorage
$ export SHIPYARD_CONFIGDIR=config_shipyard
$ shipyard pool add
$ shipyard data ingress
$ shipyard jobs add
\end{lstlisting}

Once the simulations are done (i.e., the job tasks are complete), we delete the jobs and the pool.
The output of the computation is now stored on a fileshare in our Azure Storage account and we can download the data to our local machine to perform additional post-processing steps.

\begin{lstlisting}
$ shipyard pool del
$ mkdir output
$ az storage file download-batch --source fileshare/snake2d2k25 --destination output --account-name reprostorage
\end{lstlisting}

Reproducible research requires authors to make their code and data available.
Thus, the Dockerfile and YAML configuration files should be made part of an extended reproducibility package that includes workflow instructions for cloud computing, in addition to other input files.
Such reproducibility package facilitates re-creating the cloud environment to run the simulations under the same conditions.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=14cm]{figures/cloud_workflow.png}
    \caption{Reproducible workflow on the public cloud provider Microsoft Azure.}
    \label{fig:cloud_workflow}
\end{figure*}

>>>>

\usepackage{listings}
\lstset{
    aboveskip=20pt,
    belowskip=20pt,
    lineskip=5pt,
    backgroundcolor=\color{white},
    basicstyle=\footnotesize\ttfamily,
    breakatwhitespace=true,
    breaklines=true,
    captionpos=b,
    extendedchars=true,
    frame=none,
    keepspaces=true,
    morekeywords={*,...},
    numbers=none,
    numbersep=5pt,
    rulecolor=\color{black},
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    stepnumber=2,
    tabsize=2,
    title=\lstname,
}

@@

Scientific publications reporting computational results often lack sufficient details to reproduce the researcher's computational environment; e.g., they may miss to mention external libraries used along with the main computational code.
We have learned the hard way how different versions of the same external library can alter the numerical results and even the scientific findings of a computational study\cite{mesnard_barba_2017}.
To overcome the so-called ``dependency hell'' and facilitate reproducibility, we use Docker to locally create an image of our computational application.
Container technology facilitates share build images of the full software stack that is used to produce scientific results.
The process of building an image using Docker begins with writing an ASCII file, called a Dockerfile, that contains Docker keywords and system commands for building multi-layered software stack.
Once the image is build locally, we push it to a public registry (e.g., DockerHub).
Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that has been used to run some of the examples presented in this article.
(Here, \texttt{CLOUDREPRO} is an environment variable set to path of the GitHub repository \texttt{cloud-repro}\footnote{cloud-repro: \url{https://github.com/barbargroup/cloud-repro}} cloned on a local machine.)

\begin{lstlisting}[label=lst:docker_build_push,caption={Build and push a Docker image.}]
$ cd $CLOUDREPRO/docker/petibm
$ docker build --tag=barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu --file=Dockerfile .
$ docker push barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu
\end{lstlisting}

Everyone can now pull the application image and create a Docker container to run the CFD simulation in a faithfully reproduced local environment.
We aim to move the final stage of this workflow (creating a container) to a public cloud provider such as Microsoft Azure.
\ref{fig:cloud_workflow} shows a graphical representation of the workflow we adopted to run CFD simulations with an in-house software on Microsoft Azure.

To run computational jobs on Microsoft Azure, we use several tools that facilitate creating and managing virtual machines with compute nodes and submitting jobs to those nodes.
We use a Microsoft Azure platform service called Azure Batch to run our in-house CFD software.
Azure Batch services leverages Microsoft Azure at no extra cost to relieve the user from manually creating, configuring, and managing a HPC-capable cluster of cloud nodes, including virtual machines, virtual networks, job and task scheduling infrastructure.
Azure Batch works with both embarrassingly parallel workloads and tightly-coupled MPI jobs (the latter being the case of our CFD software).
To use Azure Batch, we need to configure a workspace on Microsoft Azure.
This can be done either via the Azure Portal in a web browser or from a local terminal user the open-source tool Azure CLI.\footnote{Azure CLI (version 2.0.57): \url{https://github.com/Azure/azure-cli}}
We prefer to the use command-line solution (program \texttt{az}) as it allows us to keep track of the steps done to configure the Azure workspace (Listing \ref{lst:az_configure}).
First, we set the subscription we want to use (let's call it \texttt{reprosubscription}).
We then create a resource group, \texttt{reprorg}, located in the East US region that will contain all the Azure resources.
We create an Azure Storage account, \texttt{reprostorage}, in the resource group.
We also need to create an Azure Batch account, \texttt{reprobatch}, and associate it to the storage account.
Finally, we create a fileshare (of size $100$ Gb) in the storage.

\begin{lstlisting}[label=lst:az_configure,caption={Configure the workspace on Microsoft Azure.}]
$ az account set --subscription reprosubscription
$ az group create --name reprorg --location eastus
$ az storage account create --name reprostorage --resource-group reprorg --sku Standard_LRS --location eastus
$ az batch account create --name reprobatch --resource-group reprorg --location eastus --storage-account reprostorage
$ az storage share create --name fileshare --account-name reprostorage --account-key storagekey --quota 100
\end{lstlisting}

To create computational nodes and submit container-based jobs to Azure Batch, we use the open-source command-line utility Batch Shipyard.\footnote{Batch Shipyard (version 3.6.1): https://github.com/Azure/batch-shipyard}
Batch Shipyard is entirely driven with configuration files: the utility parses user-written YAML file to automatically create pools of compute nodes on Azure Batch and to submit jobs to those pools.
Typically, we need to provide four configuration files:

@@

Once the configuration files are written, we invoke Batch Shipyard through the \texttt{shipyard} program on our local machine.
The folder \texttt{examples/snake2d2k35/config\_shipyard} contains an example YAML files to create a pool of two compute \texttt{NC24r} nodes (that features k80 GPUs and InfiniBand network).
Listing \ref{lst:shipyard_run} shows the commands to run from your local terminal to create a pool of compute nodes on Azure Batch and submit jobs to it.
During the pool creation (\texttt{shipyard pool add}), the Docker image of our CFD application is pulled from the registry to the virtual machines.
With \texttt{shipyard data ingress}, we can upload input files to the compute nodes.
Once created, we submit jobs to the pool (\texttt{shipyard jobs add}); the tasks for a job will start automatically.

\begin{lstlisting}[label=lst:shipyard_run,caption={Create a pool with Batch Shipyard and submit jobs to it.}]
$ cd $CLOUDREPRO/examples/snake2d2k35
$ az storage directory create --name snake2d2k35 --share-name fileshare --account-name reprostorage
$ export SHIPYARD_CONFIGDIR=config_shipyard
$ shipyard pool add
$ shipyard data ingress
$ shipyard jobs add
\end{lstlisting}

Once the simulations are done (i.e., the job tasks are complete), we delete the jobs and the pool (Listing \ref{lst:shipyard_del}).
The output of the computation is now stored in the fileshare in our Azure Storage account.
We can download the data to our local machine to perform additional post-processing steps.

\begin{lstlisting}[label=lst:shipyard_del,caption={Delete the pool and jobs, and download to output to a local machine.}]
$ shipyard pool del
$ shipyard jobs del
$ mkdir output
$ az storage file download-batch --source fileshare/snake2d2k25 --destination output --account-name reprostorage
\end{lstlisting}

Reproducible research requires authors to make their code and data available.
Thus, the Dockerfile and YAML configuration files should be made part of an extended reproducibility package that includes workflow instructions for cloud computing, in addition to other input files.
Such reproducibility package facilitates re-creating the cloud environment to run the simulations under the same conditions.
The reproducibility packages of the examples showcased in the next section are available in the GitHub repository \texttt{cloud-repro}, which includes instructions on how to reproduce the results.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=14cm]{figures/cloud_workflow.png}
    \caption{Reproducible workflow on the public cloud provider Microsoft Azure. Our CFD software is version-controlled with Git and GitHub. We push to DockerHub a Docker image of our CFD application with all its dependencies. Azure-CLI is use to configure accounts on Microsof Azure and to upload/download data to/from an Azure Storage account. With Batch Shipyard, we can create pool on Azure Batch and run container-based simulation using our Docker image.}
    \label{fig:cloud_workflow}
\end{figure*}
